% =============================================================
%  Sourabrata Mukherjee — One-page CV
%  Compiles with pdflatex.  No phone number.
% =============================================================
\documentclass[10.5pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=0.65in,top=0.55in,bottom=0.55in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{ifthen}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{libertine}        % serif body — refined, scholarly
\usepackage[scaled=0.92]{inconsolata}

% colours
\definecolor{ink}{HTML}{1A1C1F}
\definecolor{accent}{HTML}{8B2F1D}
\definecolor{rule}{HTML}{C9C2B0}
\definecolor{mute}{HTML}{6F7378}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% no page numbers
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% section header — accent + thin rule
\titleformat{\section}
  {\color{accent}\large\scshape\bfseries}
  {}{0em}
  {}[\vspace{-6pt}\color{rule}\hrule height 0.5pt\vspace{2pt}]
\titlespacing*{\section}{0pt}{10pt}{4pt}

% custom rows
\newcommand{\jobrow}[4]{%
  \noindent\begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{#1}\,\textemdash\,\textit{#2} & {\color{mute}\small #3}\\
  \end{tabularx}\\[-2pt]
  \ifthenelse{\equal{#4}{}}{}{{\small #4\par\vspace{2pt}}}
}

\newcommand{\edurow}[4]{%
  \noindent\begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{#1} & {\color{mute}\small #2}\\
    \textit{#3} & \\
  \end{tabularx}\\[-2pt]
  \ifthenelse{\equal{#4}{}}{}{{\small \color{mute}#4\par\vspace{2pt}}}
}

\newenvironment{tightitem}{%
  \begin{itemize}[leftmargin=1.05em, topsep=1pt, partopsep=0pt, itemsep=1pt, parsep=0pt]
}{\end{itemize}}

% ─── header ───────────────────────────────────────────────────
\newcommand{\header}{
\begin{minipage}[t]{0.65\linewidth}
  {\fontsize{26}{30}\selectfont\textbf{\color{ink}Sourabrata Mukherjee}}\\[2pt]
  {\color{mute}\small Postdoctoral Researcher\, \textbf{·}\, Microsoft Research}\\[1pt]
  {\color{mute}\small Ph.D., Charles University, Prague}
\end{minipage}\hfill
\begin{minipage}[t]{0.34\linewidth}\raggedleft
  \small
  \href{mailto:soura1990@gmail.com}{soura1990@gmail.com}\\
  \href{https://souro.github.io}{souro.github.io}\\
  \href{https://scholar.google.com/citations?user=sYNjrdsAAAAJ}{Google Scholar}\,·\,\href{https://github.com/souro}{GitHub}\,·\,\href{https://www.linkedin.com/in/souro}{LinkedIn}
\end{minipage}
\vspace{4pt}
{\color{rule}\hrule height 0.6pt}
\vspace{6pt}
}

% =============================================================
\begin{document}
\color{ink}
\header

\section*{Research Interests}
\small Large Language Models\,·\, Multilingual \& Cultural NLP\,·\, LLM Evaluation \& LLM-as-Judge\,·\, Controllable Generation\,·\, Text Style Transfer\,·\, Low-Resource NLP\,·\, Reasoning\,·\, Conversational AI.

\section*{Education}
\edurow{Ph.D.\ in Computational Linguistics}{2019 -- 2025}{Charles University, Faculty of Mathematics and Physics, Prague}{Thesis: \emph{Text Style Transfer using Neural Models}.\, Advisor: Prof.\ Ond\v{r}ej Du\v{s}ek (UFAL).}
\vspace{3pt}
\edurow{M.Tech, Computer Science \& Engineering}{2011 -- 2013}{National Institute of Technology, Durgapur, India \,(GPA 9.06/10)}{Advisor: Prof.\ Tandra Pal. Evolutionary algorithms for GFRP composites machining and HLS data-paths.}
\vspace{3pt}
\edurow{B.Tech, Computer Science \& Engineering}{2007 -- 2011}{West Bengal University of Technology, Kolkata, India \,(GPA 8.79/10)}{}

\section*{Experience}
\jobrow{Postdoctoral Researcher}{Microsoft Research}{2026 -- present}{Language AI: multilingual and cultural NLP, LLM evaluation, controllable generation.}
\jobrow{Visiting Researcher (PhD Internship)}{MBZUAI, Abu Dhabi}{Summer 2024}{Culture \& LLM project with Prof.\ Monojit Choudhury.}
\jobrow{Research Intern}{Panlingua, India}{2022 -- 2023}{Low-resource machine translation for Indian languages.}
\jobrow{Research Assistant}{UKP Lab, TU Darmstadt, Germany}{Dec 2018 -- May 2019}{Built a data-to-text generation corpus by automatically detecting evidence linked to structured tables in scientific papers.}
\jobrow{Technical Lead}{Tricon Infotech, Bangalore}{2016 -- 2019}{Led an analytical recommendation engine driven by usage statistics.}
\jobrow{Senior Software Engineer}{Avaya Research Lab, Bangalore}{2016}{Full-stack log monitoring with optimised persistence.}
\jobrow{Software Engineer}{O9 Solutions, Bangalore}{2015 -- 2016}{Batch-job management framework with notification capability.}
\jobrow{Senior Software Engineer}{Amdocs, Pune}{2013 -- 2015}{Recommendation engine and search components for a large-scale web application.}

\section*{Selected Publications}
\begin{tightitem}
  \item \textbf{Mukherjee, S.}, Ojha, A.~K., Bansal, A., Alok, D., McCrae, J.~P., \& Du\v{s}ek, O. (2024). Multilingual Text Style Transfer: Datasets \& Models for Indian Languages. \emph{INLG 2024}.
  \item \textbf{Mukherjee, S.}, Ojha, A.~K., \& Du\v{s}ek, O. (2024). Are Large Language Models Actually Good at Text Style Transfer? \emph{INLG 2024}.
  \item \textbf{Mukherjee, S.}, Lango, M., Kasner, Z., \& Du\v{s}ek, O. (2024). A Survey of Text Style Transfer: Applications and Ethical Implications. \emph{NEJLT}.
  \item \textbf{Mukherjee, S.}, Bansal, A., Majumdar, P., Ojha, A.~K., \& Du\v{s}ek, O. (2023). Low-Resource Text Style Transfer for Bangla. \emph{BLP @ EMNLP 2023.} \,\textcolor{accent}{[Best Paper Award]}
  \item \textbf{Mukherjee, S.}, Bansal, A., Ojha, A.~K., McCrae, J.~P., \& Du\v{s}ek, O. (2023). Text Detoxification as Style Transfer in English and Hindi. \emph{ICON 2023}.
  \item \textbf{Mukherjee, S.}, \& Du\v{s}ek, O. (2023). Leveraging Low-resource Parallel Data for Text Style Transfer. \emph{INLG 2023}.
  \item \textbf{Mukherjee, S.}, Hude\v{c}ek, V., \& Du\v{s}ek, O. (2023). Polite Chatbot: A Text Style Transfer Application. \emph{EACL 2023 Student Research Workshop}.
  \item \textbf{Mukherjee, S.}, Kasner, Z., \& Du\v{s}ek, O. (2022). Balancing the Style-Content Trade-off in Sentiment Transfer using Polarity-Aware Denoising. \emph{TSD 2022}.
\end{tightitem}

\section*{Awards \& Service}
\begin{tightitem}
  \item \textbf{Best Paper Award}, BLP Workshop, EMNLP 2023.
  \item \textbf{GAUK Research Grant} (Charles University Grant Agency) as PI; completed with \emph{honourable mention}.
  \item \textbf{GATE Scholarship}, Government of India, for the Graduate Aptitude Test in Engineering.
  \item \textbf{Winner}, IBM National-level Technical Competition.
  \item Taught introductory courses on Machine Learning, Deep Learning, Programming, and Data Structures.
\end{tightitem}

\end{document}
